Democratizing Secure Two-Party Computation

### 2017-10-17 OaklandSubmission/eval.tex
seahorn
minor

\section{Evaluation}
\label{sec:eval}
We evaluate \tool for the problem of {\it secure prediction}, where a server has a machine learning model, a client has an input, and after the protocol execution the client learns a label on his input.
From the protocol execution, the server learns nothing about the client's input and the client learns nothing about the server's model beyond what is revealed from the computed label.
This setting has been previously studied in~\cite{shafindss,minionn}
We first implement benchmarks of ~\cite{shafindss} and~\cite{minionn} in \tool to compare against 
previous work.
Next, we demonstrate the generality of \tool by implementing state-of-the-art machine learning models.
Finally, we discuss a model that requires pipelinig.
Our results are in two settings, a LAN setting and a cross-continent WAN setting.
The round trip time for two machines in a LAN setting is 1ms and in WAN setting is 40ms.
Each machine has a Intel(R) Xeon(R) CPU E5-2673 v3 processor running at 2.40GHz with
28 GBs of RAM. The \tool compiler is written in Python and compiles each of our benchmarks
in under a second to C++ code that makes calls to the ABY library~\cite{aby}. Since most of our benchmarks are related to machine learning, we set up some notation standard to machine learning and describe our benchmarks next.

@@

\noindent\textbf{Notation.} We use $[N]$ to denote $\{0,1,\dotsc, N-1\}$. \rs{Define $\mathsf{argmax}$.}

@@

A more interesting classifier is Na\"{i}ve Bayes that predicts labels from the set $[n]$.
Here, the input data point is a {\it feature}
vector $x=(x_0,x_2,\ldots,x_{d-1})^T$ where each $x_j\in [F]$.
The model has two matrices: a vector $P$ of length $n$ and for each $i \in [n]$, $P(i)$ is the log-probability that the output label is $i$.
%$P(i) \equiv \log p(\ell=i)$, where $p(\ell=i)$ is the likelihood that the output label is $i$ for $i\in[n]$.
The other matrix $T$ has size $n\times d\times F$ and for each $i\in [n], j\in [d], k\in [F]$, $T(i)(j)(k)$ is
%\equiv\log p(x_j|\ell=i)$, i.e., 
the log-probability that  the $j^{th}$ input feature is $k$  conditioned on  the output label being $i$.
The classifier $C_{P,T}(x)$ outputs
\[
{\sf argmax}_i P(i)+\sum_{j=0}^{d-1} T(i)(j)(x_j)
\]
This classifier requires $ndF$ comparisons and additions. \divya{Note that computing $T(i)(j)(x_j)$ requires a secret look-up in matrix $T$  based on secret input $x_j$ resulting in $F$ comparisons (see \sectionref{}).} \cmmt{Is there a +1 etc missing or is this exact?}

@@

Finally, there are a class of machine learning classifiers that are much more efficient than
DNNs and provide reasonably good accuracies on standard learning tasks. One such classifier
is \bonsai~\cite{bonsai} that takes as input $x \in \R^d$ and model consists of a binary tree with $N$ nodes. Each node $j$ contains matrices $W_j$ and $V_j$. The internal node $j$  evaluates a predicate $\theta_j^TZx > 0$ to decide whether
to pass $x$ to the left child $2j+1$ or the right child $2j+2$ (where $\theta_j$ is a vector and $Z$ is a matrix).
The predicted value is
\[
{\sf argmax} \sum_{j\in [N]} I_j(x)W_j^TZx\circ f(V_j^TZx) 
\]
Here, $I_j(x)$ is 1 if the $j^{th}$ node is present on the path traversed by $x$
and is zero otherwise. 
The operation $\circ$ is a point-wise dot product, $W_j$'s and $V_j$'s are matrices. The activation function $f$ is given by $f(y) = y$ if $-1 < y < 1$ and $\mathrm{sign}(x)$ otherwise. The model consists of the matrices $W_j$, $V_j$, $Z$ and vectors $\theta_j$. \bonsai can be seen as a variant of decision trees where the prediction is a function of the path traversed from root to the leaf and not just the leaf itself.

@@

For the benchmarks in Table~\ref{tab:nn}, \minion
outperforms SecureML and Cryptonets and columns 2 and 3 show the time taken by \minion. 
The column ``Model size'' is the number of 32 bit integers in the trained model.
We observe that our performance is competitive with \minion in the LAN and the WAN settings and the lines of code required are still small.
We note that \minion and \tool implementations are both based on ABY.
These results are surprising as \minion has a much more efficient preprocessing phase and has SIMD
(single instruction multiple data) capabilities that allow \minion to perform
matrix operations efficiently. Our language and compiler are generic and we have none of these.
Although we could have used the SIMD capabilities of ABY to improve our performance---our preliminary evaluation suggests that SIMD could lead to a 2X performance improvement---we decided against it to avoid being closely tied to ABY and keeping \tool general, i.e., oblivious to the 2PC backend.
However, \minion also reports performance results on a bigger DNN with 7 convolution layers.
This benchmark requires pipelining and we discuss it in Section~\ref{sec:pipeeval}.
%net | minionT | minionC | timeL | timeW | comm | gates | and | mul | length

\begin{table*}
\begin{tabular}{c|c|c|c |c|c|c|c|c|c|c}
Name  & Prev. time (s) & Prev. Comm (Mb) & LAN time (s) & WAN time (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates & Model Size & LOC\\
\hline
SecureML   &  1.1 & 15.8 & 0.7 & 1.7  & 76   &  2k   & 119k & 366k   & 119k & 78\\
\hline
Cryptonets &  1.3 & 47.6 & 0.6 & 1.6  & 7    & 2k    & 108k & 316k & 86k & 88\\
\hline
CNN        &  9.4 & 657.5& 5.1 & 11.6 & 501  & 1640k & 667k & 9480k & 35k & 154\\
\hline
\end{tabular}

@@

\begin{table*}
\begin{tabular}{c|c|c|c |c|c|c|c|c|c | c}
Name       & LAN time (s) & WAN time (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates & Model size & LOC\\
\hline
Regression &  0.1         & 0.7         & 5            & 2k    & 8k    &  35k    & 8k   & 38\\
\hline
CNN        &  30.5        & 60.3        & 2955         & 6082k & 4163k &  42104k & 3226k& 172\\
\hline
\end{tabular}

@@

\begin{table*}
\begin{tabular}{c|c|c|c |c|c|c|c|c|c | c}
Name       & LAN time (s) & WAN time (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates & depth & LOC\\
\hline
Chars4k    &  0.1         & 0.7         & 2            & 18k    & 3k    &  85k     & 1   & 89\\
\hline
USPS       &  0.2         & 0.9         & 4            & 62k    & 2k    &  285k    & 2   & 156\\
\hline
WARD       &  0.3         & 1.1         & 9            & 106k    & 8k    &  506k    & 3   & 283\\
\hline
\end{tabular}

@@

 \caption{Pipelining results}
 \label{tab:cifar} 
\end{table}

>>>>

\section{Evaluation}
\label{sec:eval}
We evaluate \tool for the problem of {\it secure prediction}, where a server has a machine learning model, a client has an input, and after the protocol execution the client learns a label on his input.
From the protocol execution, the server learns nothing about the client's input and the client learns nothing about the server's model beyond what is revealed from the computed label.
This setting has been previously studied in~\cite{shafindss,minionn}
We first implement benchmarks of ~\cite{shafindss} and~\cite{minionn} in \tool to compare against 
previous work.
Next, we demonstrate the generality of \tool by implementing state-of-the-art machine learning models.
Finally, we discuss a model that requires pipelinig.
Our results are in two settings, a LAN setting and a cross-continent WAN setting.
The round trip time for two machines in a LAN setting is 1ms and in WAN setting is 40ms.
Each machine has a Intel(R) Xeon(R) CPU E5-2673 v3 processor running at 2.40GHz with
28 GBs of RAM. The \tool compiler is written in Python and compiles each of our benchmarks
in under a second to C++ code that makes calls to the ABY library~\cite{aby}.
We use an off-the-shelf solver (SeaHorn~\cite{seahorn}) to check the verification conditions
required to prove that the array indices remain in bound.
The solver takes less than a minute on our largest benchmark.
Since most of our benchmarks are related to machine learning, we set up some notation standard to machine learning and describe our benchmarks next.

@@

\noindent\textbf{Notation.} We use $[N]$ to denote $\{0,1,\dotsc, N-1\}$. 
Given a vector $x\in\R^d$, $\mathsf{argmax}\ x = i$ if $x(i) = \mathsf{max}\ \{x_1,\ldots,x_d\}$

@@

A more interesting classifier is Na\"{i}ve Bayes that predicts labels from the set $[n]$.
Here, the input data point is a {\it feature}
vector $x=(x_0,x_2,\ldots,x_{d-1})^T$ where each $x_j\in [F]$.
The model has two matrices: a vector $P$ of length $n$ and for each $i \in [n]$, $P(i)$ is the log-probability that the output label is $i$.
%$P(i) \equiv \log p(\ell=i)$, where $p(\ell=i)$ is the likelihood that the output label is $i$ for $i\in[n]$.
The other matrix $T$ has size $d\times F\times n$ and for each $j\in [d], k\in [F], i\in [n]$, $T(j)(k)(i)$ is
%\equiv\log p(x_j|\ell=i)$, i.e., 
the log-probability that  the $j^{th}$ input feature is $k$  conditioned on  the output label being $i$.
The classifier $C_{P,T}(x)$ outputs
\[
{\sf argmax}\ P+\sum_{j=0}^{d-1} T(j)(x_j)
\]
This classifier requires $ndF$ comparisons and additions. \divya{Note that computing $T(i)(j)(x_j)$ requires a secret look-up in matrix $T$  based on secret input $x_j$ resulting in $F$ comparisons (see \sectionref{}).} \cmmt{Is there a +1 etc missing or is this exact?}

@@

Finally, there are a class of machine learning classifiers that are much more efficient than
DNNs and provide reasonably good accuracies on standard learning tasks. \bonsai~\cite{bonsai} is a state-of-the art classifier in this class and \tool provides the first 2PC protocol for it.
\bonsai takes as input $x \in \R^d$ and model consists of a binary tree with $N$ nodes. Each node $j$ contains matrices $W_j$ and $V_j$. The internal node $j$  evaluates a predicate $\theta_j^TZx > 0$ to decide whether
to pass $x$ to the left child $2j+1$ or the right child $2j+2$ (where $\theta_j$ is a vector and $Z$ is a matrix).
The predicted value is
\[
{\sf argmax} \sum_{j\in [N]} I_j(x)W_j^TZx\circ f(V_j^TZx) 
\]
Here, $I_j(x)$ is 1 if the $j^{th}$ node is present on the path traversed by $x$
and is zero otherwise. 
The operation $\circ$ is a point-wise dot product, $W_j$'s and $V_j$'s are matrices. The activation function $f$ is given by $f(y) = y$ if $-1 < y < 1$ and $\mathrm{sign}(x)$ otherwise. The model consists of the matrices $W_j$, $V_j$, $Z$ and vectors $\theta_j$. \bonsai can be seen as a variant of decision trees where the prediction is a function of the path traversed from root to the leaf and not just the leaf itself.

@@

For the benchmarks in Table~\ref{tab:nn}, \minion
outperforms SecureML and Cryptonets and columns 2 and 3 show the time taken by \minion. 
The column ``Model size'' is the number of 32 bit integers in the trained model.
We observe that our performance is competitive with \minion in the LAN and the WAN settings and the lines of code required are still small.
We note that \minion and \tool implementations are both based on ABY.
These results are surprising as \minion has a much more efficient preprocessing phase and has SIMD
(single instruction multiple data) capabilities that allow \minion to perform
matrix operations efficiently. Our language and compiler 
focus on generic 2PC and such optimizations are beyond the scope of this paper.
However, \minion also reports performance results on a bigger DNN with 7 convolution layers.
This benchmark requires pipelining and we discuss it in Section~\ref{sec:pipeeval}.
%net | minionT | minionC | timeL | timeW | comm | gates | and | mul | length

\begin{table*}
\begin{tabular}{c|c|c|c |c|c|c|c|c|c|c}
DNN  & Prev. time (s) & Prev. Comm (Mb) & LAN time (s) & WAN time (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates & Model Size & LOC\\
\hline
SecureML   &  1.1 & 15.8 & 0.7 & 1.7  & 76   &  2k   & 119k & 366k   & 119k & 78\\
\hline
Cryptonets &  1.3 & 47.6 & 0.6 & 1.6  & 70    & 2k    & 108k & 316k & 86k & 88\\
\hline
CNN        &  9.4 & 657.5& 5.1 & 11.6 & 501  & 1640k & 667k & 9480k & 35k & 154\\
\hline
\end{tabular}

@@

\begin{table*}
\begin{tabular}{c|c|c|c |c|c|c|c|c|c | c}
Classifier       & LAN time (s) & WAN time (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates & Model size & LOC\\
\hline
Regression &  0.1         & 0.7         & 5            & 2k    & 8k    &  35k    & 8k   & 38\\
\hline
CNN        &  30.5        & 60.3        & 2955         & 6082k & 4163k &  42104k & 3226k& 172\\
\hline
\end{tabular}

@@

\begin{table*}
\begin{tabular}{c|c|c|c |c|c|c|c|c|c | c}
Dataset       & LAN time (s) & WAN time (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates & depth & LOC\\
\hline
Chars4k    &  0.1         & 0.7         & 2            & 18k    & 3k    &  85k     & 1   & 89\\
\hline
USPS       &  0.2         & 0.9         & 4            & 62k    & 2k    &  285k    & 2   & 156\\
\hline
WARD       &  0.3         & 1.1         & 9            & 106k    & 8k    &  506k    & 3   & 283\\
\hline
\end{tabular}

@@

 \caption{Pipelining results for CIFAR-10. \minion takes 544 seconds and communicates 9272 Mb to evaluate this DNN.}
 \label{tab:cifar} 
\end{table}
